---
title: "Webcam analysis"
shorttitle: "Webcam analysis"
author:
  - name: First Author
    corresponding: true
    orcid: 0000-0000-0000-0001
    email: janedoe@generic.edu
    affiliations:
      - name: Generic University
        department: Department
        address: 1234 Capital St.
        city: New York
        region: NY
        country: USA
        postal-code: 12084-1234
author-note:
  status-changes: 
    affiliation-change: null
    deceased: null
  disclosures:
    study-registration: null
    data-sharing: null
    related-report: null
    conflict-of-interest: null
    financial-support: null
    gratitude: null
    authorship-agreements: null
abstract: "This document is a template."
impact-statement: "This template helps you get started."
keywords: [Keyword 1, Keyword 2, Keyword 3]
bibliography: ["bibliography.bib", "r-references.bib"]
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-typst: default
  apaquarto-pdf:
    documentmode: man
editor_options: 
  chunk_output_type: inline
---

```{r}
#| label: setup
#| include: false
library(conflicted)
library(tidyverse)
library(dplyr)
library(qs2)
library(gt)
#library(gtsummary)
#library(flextable)
#library(ftExtra)
library(knitr)
#library(kableExtra)
library(here)
#library(simr)
# we only use papaja here for the R package citation functions (r_refs and cite_r)
library(papaja)
library(tidybayes)
#library(marginaleffects)
library(emmeans)
library(sjPlot)
library(modelsummary)


conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(dplyr::select, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)

ctr <- function(x) scale(x, scale = FALSE)

source("brms_effect_summary.R")

# this is a fix for an issue in r_refs with papaja: [https://github.com/crsh/papaja/issues/608](https://github.com/crsh/papaja/issues/608)
source("validate.R")
source("r_refs_fixed.R")
# hopefully, this can be removed once papaja is updated
r_refs(here("manuscript","r-references.bib"), append = FALSE)

# convenience function to format descriptive summary statistics as "mean (sd)"
print_mean_sd <- function(datum, digits_mean = 0, digits_sd = 2){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)) %>% format_value(digits = digits_sd)})")
}

# convenience function to format inferential summary statistics as "mean (se)"
print_mean_se <- function(datum, digits_mean = 0, digits_se = 2){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)/sqrt(length(datum))) %>% format_value(digits = digits_se)})")
}

# convenience function to format range summary statistics as "min -- max"
print_range <- function(datum, digits_min = 2, digits_max = 2){
  str_glue("({min(datum) %>% format_value(digits = digits_min)} -- {max(datum) %>% format_value(digits = digits_max)})")
}

print_mean_sd_range <- function(datum, digits_mean = 2, digits_sd = 2, digits_min = 0, digits_max = 0){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)) %>% format_value(digits = digits_sd)}; {min(datum) %>% format_value(digits = digits_min)} -- {max(datum) %>% format_value(digits = digits_max)})")
}

# format value for in-text statistics
format_value <- function(value) {
    if (is.na(value) || !is.numeric(value)) {
      return(as.character(value))
    }
    if (abs(value) < 0.01 && value != 0) {
      return(formatC(value, format = "g", digits = 2))
    } else {
      return(format(round(value, 2), nsmall = 2))
    }
  }

make_gtsummary_table_for_target_word_brm <- function(brmsfit) {
  tbl_regression(brmsfit, exponentiate = FALSE, intercept = TRUE,label = list(`Freq` ~ "Frequency", `Tracker` ~ "Eye tracker", `factor(Freq):factor(Tracker(` ~ "Interaction"), show_single_row = any_of(c("Freq", "Tracker")),
                 estimate_fun = ~style_sigfig(., digits = 3)) %>%
    modify_table_styling(
      columns = c(estimate, conf.low),
      rows = !(0 >= conf.low & 0 <= conf.high),
      text_format = "bold") %>%
    modify_header(label = "**Variable**", estimate = "**b**", conf.low = "**CrI**") %>%
    modify_abbreviation("CrI = 95% Credible Interval") %>%
    remove_abbreviation("CI = Credible Interval")
}

```



This is my first paragraph. Any section headings in the introduction should be in levels 2--5.

## Section in Introduction

This is a reference [@cohen2003applied].

## Experiment 1

### Method

### Participants

### Measures

### Procedure

### Data analysis

We analysed the data for the frequency corpus by fitting Bayesian linear mixed models using the brms package [@R-brms_a; @R-brms_b; @R-brms_c] in R^[The versions of R and all packages used are as follows: `r papaja::cite_r("r-references.bib")`.]. These models included the word frequency condition (low, represented as -.5, vs. high, represented as .5) as well as the eye-tracker used (with the Eyelink represented as -.5 and the Webcam represented as .5). We included the maximum random effects structure [i.e., random intercepts and random slopes for condition, stimulus type, and their interaction over subjects and random intercepts and random slopes for condition over items, @barr2013]. We used the Gaussian distribution to model fixation times, after excluding excessively short (< 80 ms) and long observations (first fixation duration and single fixation duration > 1,000 ms; gaze duration > 1,800 ms; total viewing time > 2,000). We used the default priors suggested by brms for the fixed effects and random effects; coefficients were given weakly informative priors to rule out implausibly large effects. Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations. The models converged successfully (all R-hats = 1.00). We report the estimates (b) and the 95% Bayesian Credible Intervals (95% CIs) based on the posterior distribution of each model parameter and indicate whether 0 is excluded from the 95% CI. Additionally, we report the proportion of the posterior on the same side of 0 ($P(b > 0)$ or $P(b < 0$) and its ratio to the opposite-side proportion as a directional evidence ratio ($ER_{b>0}$ or $ER_{b<0}$), which can be interpreted as a Bayes factor for the directional hypothesis. Finally, we report Savage–Dickey Bayes factors for the point-null hypothesis b = 0 [$BF_{10}$, @jeffreys1961]. It is important to note that each of these statistics is a valid way to summarize the evidence provided by the data, but, for simplicity, we will focus on the 95% CI in our verbal description of the results. 

### Results

#### Target word analysis

```{r}
#| label: load-exp1-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the fixation time measures
target_words_exp1 <- read_csv(here("LAB/data/target_word_fixation_data.csv")) %>%
  mutate(Freq = factor(Freq, levels = c("low", "high")),
         Tracker = factor(Tracker, levels = c("Webcam", "Eyelink")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp1 <- read_csv(here("LAB/data/corpus_fixation_data.csv")) %>%
  mutate(Tracker = factor(Tracker, levels = c("Eyelink", "Webcam")),
         item = factor(item),
         sub = factor(sub))

# load the Gaussian model results
blmm_target_FFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_FFD_exp1_gaussian.qs"))
blmm_target_SFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_SFD_exp1_gaussian.qs"))
blmm_target_GD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_GD_exp1_gaussian.qs"))
blmm_target_TVT_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_TVT_exp1_gaussian.qs"))
blmm_target_skip_exp1 <- qs_read(here("LAB", "models", "brms", "blmm_target_skip_exp1.qs"))


# prepare effect summaries (μ component only)
blmm_target_FFD_exp1_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp1_gaussian, "Freq1")
blmm_target_FFD_exp1_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp1_gaussian, "Tracker1")
blmm_target_FFD_exp1_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp1_gaussian, "Freq1:Tracker1")

blmm_target_GD_exp1_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp1_gaussian, "Freq1")
blmm_target_GD_exp1_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp1_gaussian, "Tracker1")
blmm_target_GD_exp1_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_GD_exp1_gaussian, "Freq1:Tracker1")

blmm_target_SFD_exp1_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp1_gaussian, "Freq1")
blmm_target_SFD_exp1_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp1_gaussian, "Tracker1")
blmm_target_SFD_exp1_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp1_gaussian, "Freq1:Tracker1")

blmm_target_TVT_exp1_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp1_gaussian, "Freq1")
blmm_target_TVT_exp1_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp1_gaussian, "Tracker1")
blmm_target_TVT_exp1_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp1_gaussian, "Freq1:Tracker1")

blmm_target_skip_exp1_mu_Freq1_effect <- brms_effect_summary(blmm_target_skip_exp1, "Freq1")
blmm_target_skip_exp1_mu_Tracker1_effect <- brms_effect_summary(blmm_target_skip_exp1, "Tracker1")
blmm_target_skip_exp1_mu_interaction_effect <- brms_effect_summary(blmm_target_skip_exp1, "Freq1:Tracker1")

# estimated marginal means: low - high within each tracker
format_contrast_string <- function(data) {
  tracker_strings <- data %>%
    mutate(
      report_string = sprintf(
        "%s: *M* = %.2f 95%% *CI* = [%.2f, %.2f]",
        Tracker,
        .value,
        .lower,
        .upper
      )
    ) %>%
    pull(report_string)
  sprintf("%s", str_c(tracker_strings, collapse = "; "))
}

marginal_effects_exp1_target_FFD <- emmeans(blmm_target_FFD_exp1_gaussian, ~ Freq | Tracker) %>%
  pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_target_GD <- emmeans(blmm_target_GD_exp1_gaussian, ~ Freq | Tracker) %>%
  pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_target_SFD <- emmeans(blmm_target_SFD_exp1_gaussian, ~ Freq | Tracker) %>%
  pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_target_TVT <- emmeans(blmm_target_TVT_exp1_gaussian, ~ Freq | Tracker) %>%
  pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_target_skip <- emmeans(blmm_target_skip_exp1, ~ Freq | Tracker) %>%
  pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_string_exp1_target_FFD <- format_contrast_string(marginal_effects_exp1_target_FFD)
marginal_effects_string_exp1_target_SFD <- format_contrast_string(marginal_effects_exp1_target_SFD)
marginal_effects_string_exp1_target_GD <- format_contrast_string(marginal_effects_exp1_target_GD)
marginal_effects_string_exp1_target_TVT <- format_contrast_string(marginal_effects_exp1_target_TVT)
marginal_effects_string_exp1_target_Skip <- format_contrast_string(marginal_effects_exp1_target_skip)
```

```{r}
#| label: tbl-exp1-target-word-means
#| echo: false
#| message: false
#| after-caption-space: 0pt
#| tbl-cap: "Mean first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD),  total viewing time (TVT), and skipping probability on target words in Experiment 1 by eye-tracker and word frequency condition."

target_words_exp1_means_table <- target_words_exp1 %>%
  group_by(Tracker, Freq) %>%
  summarise(
    mean_FFD = mean(FFD, na.rm = TRUE),
    sd_FFD = sd(FFD, na.rm = TRUE),
    mean_SFD = mean(SFD, na.rm = TRUE),
    sd_SFD = sd(SFD, na.rm = TRUE),
    mean_GD = mean(GD, na.rm = TRUE),
    sd_GD = sd(GD, na.rm = TRUE),
    mean_TVT = mean(TVT, na.rm = TRUE),
    sd_TVT = sd(TVT, na.rm = TRUE),
    mean_skip= mean(skip_first_pass, na.rm= TRUE),
    sd_skip= sd(skip_first_pass, na.rm= TRUE)
  ) %>%
  ungroup()

target_words_exp1_means_table %>%
  gt(rowname_col = "Tracker") %>%
  cols_label(
   starts_with("mean") ~ "Mean",
   starts_with("sd") ~ "SD",
   "Freq" ~ "Frequency"
  ) %>%
  tab_spanner(label = "FFD", columns = ends_with("FFD")) %>%
  tab_spanner(label = "SFD", columns = ends_with("SFD")) %>%
  tab_spanner(label = "GD", columns = ends_with("GD")) %>%
  tab_spanner(label = "TVT", columns = ends_with("TVT")) %>%
  tab_spanner(label = "Skip", columns = ends_with("skip")) %>%
  # All non-skip columns → 0 decimals
  fmt_number(
    columns = -ends_with("skip"),
    decimals = 0
  ) %>%
  
  # Skip columns → 2 decimals
  fmt_number(
    columns = ends_with("skip"),
    decimals = 2
  ) %>%
  tab_stubhead(label = "Tracker") %>%
  tab_source_note(source_note = md("Note: *FFD* = first fixation duration; *SFD* = single fixation duration; *GD* = gaze duration; *TVT* = total viewing time; SD = standard deviation. All means and standard deviations are reported in milliseconds (ms)."))
```

@tbl-exp1-target-word-means shows the mean and standard deviation of first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1 by eye-tracker and word frequency condition, while @tbl-exp1-target-modelsummary shows the model estimates.

```{r}
#| label: tbl-exp1-target-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1."

coef_map <- c("b_Intercept" = "Intercept",
              "b_Freq1" = "Frequency",
              "b_Tracker1" = "Tracker",
              "b_Freq1:Tracker1" = "Frequency × Tracker")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_target_FFD_exp1_gaussian, SFD = blmm_target_SFD_exp1_gaussian, GD = blmm_target_GD_exp1_gaussian, TVT = blmm_target_TVT_exp1_gaussian, Skip= blmm_target_skip_exp1),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT", "Skip"))
```

Overall, low-frequency words elicited longer fixation times than high-frequency words across all measures (FFD: `r blmm_target_FFD_exp1_gaussian_mu_Freq1_effect`; SFD: `r blmm_target_SFD_exp1_gaussian_mu_Freq1_effect`; GD: `r blmm_target_GD_exp1_gaussian_mu_Freq1_effect`; TVT: `r blmm_target_TVT_exp1_gaussian_mu_Freq1_effect`). Low frequency words led to lower skipping probability, though the credible interval narrowly included 0: `r blmm_target_skip_exp1_mu_Freq1_effect`. Fixation times were also longer with the Webcam than with the Eyelink and skipping rates were similarly higher (FFD: `r blmm_target_FFD_exp1_gaussian_mu_Tracker1_effect`; SFD: `r blmm_target_SFD_exp1_gaussian_mu_Tracker1_effect`; GD: `r blmm_target_GD_exp1_gaussian_mu_Tracker1_effect`; TVT: `r blmm_target_TVT_exp1_gaussian_mu_Tracker1_effect`; Skipping: `r blmm_target_skip_exp1_mu_Tracker1_effect`). This is likely due to a systematic difference in the saccade and fixation detection algorithms. Importantly, the Frequency × Tracker interaction was not credibly different from 0 (FFD: `r blmm_target_FFD_exp1_gaussian_mu_interaction_effect`; SFD: `r blmm_target_SFD_exp1_gaussian_mu_interaction_effect`; GD: `r blmm_target_GD_exp1_gaussian_mu_interaction_effect`; TVT: `r blmm_target_TVT_exp1_gaussian_mu_interaction_effect`; Skipping: `r blmm_target_skip_exp1_mu_interaction_effect`), indicating that the frequency effect was comparable across devices.

The absence of an interaction between frequency and tracker is not positive evidence for a frequency effect in the Webcam data on its own. We calculated posterior distributions for the estimated marginal means of the difference between low and high frequency target words and found that the 95% credible intervals for these differences in the Webcam data included 0, while the credible intervals for the Eyelink data excluded 0 in FFD (`r marginal_effects_string_exp1_target_FFD`), SFD (`r marginal_effects_string_exp1_target_SFD`), GD (`r marginal_effects_string_exp1_target_GD`),
Skipping (`r marginal_effects_string_exp1_target_Skip`), and TVT (`r marginal_effects_string_exp1_target_TVT`), although the CI for the latter included 0 very narrowly. This indicates that, while the webcam data is consistent with a frequency effect of a similar magnitude to that observed with the Eyelink, the evidence is not sufficiently strong to confirm the presence of frequency effect based on the Webcam data alone using the criterion of the 95% credible interval excluding 0. We assume that this is due to the higher amount of noise in the Webcam data.

#### Corpus-style analysis

By including all words in every sentence into the analysis, rather than only the target words, we can increase the number of observations. Of course, this comes at the cost of increased variability due to differences in word length, predictability, and other lexical and contextual factors, but, overall, this approach is likely to have a better chance to detect the word frequency effect. 
@tbl-exp1-corpus-modelsummary shows the results of these "corpus-analysis style" Bayesian linear mixed models with Zipf frequency as a continuous predictor, tracker as a two-level factor (as in the target-word analysis) and the interaction between the two predictors for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT) on all words in the sentences (except for the first and last word in each sentence) in Experiment 1.


```{r}
#| label: load-exp1-corpus-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the Gaussian corpus model results
blmm_corpus_FFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_FFD_exp1_gaussian.qs"))
blmm_corpus_SFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_SFD_exp1_gaussian.qs"))
blmm_corpus_GD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_GD_exp1_gaussian.qs"))
blmm_corpus_TVT_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_TVT_exp1_gaussian.qs"))

# emtrends for frequency slopes by tracker (Zipf slope within device)
marginal_effects_exp1_corpus_FFD <- emtrends(blmm_corpus_FFD_exp1_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_GD <- emtrends(blmm_corpus_GD_exp1_gaussian, "Tracker", "zipf")  %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_SFD <- emtrends(blmm_corpus_SFD_exp1_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_TVT <- emtrends(blmm_corpus_TVT_exp1_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_string_exp1_corpus_FFD <- format_contrast_string(marginal_effects_exp1_corpus_FFD)
marginal_effects_string_exp1_corpus_GD <- format_contrast_string(marginal_effects_exp1_corpus_GD)
marginal_effects_string_exp1_corpus_SFD <- format_contrast_string(marginal_effects_exp1_corpus_SFD)
marginal_effects_string_exp1_corpus_TVT <- format_contrast_string(marginal_effects_exp1_corpus_TVT)
```

```{r}
#| label: tbl-exp1-corpus-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on all words (except for the first and last in each sentence) in Experiment 1."

coef_map_corpus <- c("b_Intercept" = "Intercept",
              "b_ctrzipf" = "Zipf frequency",
              "b_Tracker1" = "Tracker",
              "b_ctrzipf:Tracker1" = "Frequency × Tracker")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_corpus_FFD_exp1_gaussian, SFD = blmm_corpus_SFD_exp1_gaussian, GD = blmm_corpus_GD_exp1_gaussian, TVT = blmm_corpus_TVT_exp1_gaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map_corpus,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

As expected we observed a frequency effect in that a higher Zipf frequency (i.e., more frequent words) was associated with shorter fixation times across all measures (FFD: `r brms_effect_summary(blmm_corpus_FFD_exp1_gaussian, "ctrzipf")`; SFD: `r brms_effect_summary(blmm_corpus_SFD_exp1_gaussian, "ctrzipf")`; GD: `r brms_effect_summary(blmm_corpus_GD_exp1_gaussian, "ctrzipf")`; TVT: `r brms_effect_summary(blmm_corpus_TVT_exp1_gaussian, "ctrzipf")`). We again observed longer mean fixation times with the Webcam than with the Eyelink (FFD: `r brms_effect_summary(blmm_corpus_FFD_exp1_gaussian, "Tracker1")`; SFD: `r brms_effect_summary(blmm_corpus_SFD_exp1_gaussian, "Tracker1")`; GD: `r brms_effect_summary(blmm_corpus_GD_exp1_gaussian, "Tracker1")`; TVT: `r brms_effect_summary(blmm_corpus_TVT_exp1_gaussian, "Tracker1")`). There were small, but credible Frequency × Tracker interactions in FFD (`r brms_effect_summary(blmm_corpus_FFD_exp1_gaussian, "ctrzipf:Tracker1")`), SFD (`r brms_effect_summary(blmm_corpus_SFD_exp1_gaussian, "ctrzipf:Tracker1")`), GD (`r brms_effect_summary(blmm_corpus_GD_exp1_gaussian, "ctrzipf:Tracker1")`), and TVT (`r brms_effect_summary(blmm_corpus_TVT_exp1_gaussian, "ctrzipf:Tracker1")`), indicating that the frequency effect was stronger in the Eyelink data compared to the Webcam data. In order to show the marginal effect of zipf frequency within each device directly, we summarized the slope of the zipf effect using `emtrends` from the `emmeans` package. We found consistent evidence for the frequency effect in all measures for both the Eyelink and the Webcam (FFD: `r marginal_effects_string_exp1_corpus_FFD`, SFD: `r marginal_effects_string_exp1_corpus_SFD`, GD: `r marginal_effects_string_exp1_corpus_GD`, TVT: `r marginal_effects_string_exp1_corpus_TVT`).
Overall, this demonstrates that, when there is sufficient data, the frequency effect can be detected even in the noisier Webcam data.

## Experiment 2

### Method

#### Participants

#### Measures

#### Procedure

#### Data analysis

The model specifications and data analysis were the same as in Experiment 1.

### Results

```{r}
#| label: load-exp2-target-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the fixation time measures
target_words_exp2 <- read_csv(here("LAB-SPAIN/data/target_word_fixation_data.csv")) %>%
  mutate(Freq = factor(Freq, levels = c("low", "high")),
         Tracker = factor(Tracker, levels = c("Webcam", "Eyelink")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp2 <- read_csv(here("LAB-SPAIN/data/all_words_fixation_data.csv")) %>%
  mutate(Tracker = factor(Tracker, levels = c("Eyelink", "Webcam")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp2 <- corpus_words_exp2 %>% 
  mutate(position = case_when(grepl("\\.$", wordID) & word_num == max(word_num) ~ "last", 
                              word_num == 1 ~ "first", 
                              TRUE ~ "middle"),
         word_code = paste(item, word_num, sep = "_"),
         len = nchar(wordID))

exp2_word_frequency_data <- read_tsv(here("LAB-SPAIN/spanish_corpus_words_with_frequencies_espal.txt")) %>% select(word,frq,zipf,num_letters)

corpus_words_exp2 <- corpus_words_exp2 %>%
  left_join(exp2_word_frequency_data, by = c("wordID" = "word"))

# load the Gaussian target-word models
blmm_target_FFD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_FFD_exp2_gaussian.qs"))
blmm_target_SFD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_SFD_exp2_gaussian.qs"))
blmm_target_GD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_GD_exp2_gaussian.qs"))
blmm_target_TVT_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_TVT_exp2_gaussian.qs"))

# prepare effect summaries (μ component only)
blmm_target_FFD_exp2_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp2_gaussian, "Freq1")
blmm_target_FFD_exp2_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp2_gaussian, "Tracker1")
blmm_target_FFD_exp2_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp2_gaussian, "Freq1:Tracker1")

blmm_target_GD_exp2_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp2_gaussian, "Freq1")
blmm_target_GD_exp2_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp2_gaussian, "Tracker1")
blmm_target_GD_exp2_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_GD_exp2_gaussian, "Freq1:Tracker1")

blmm_target_SFD_exp2_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp2_gaussian, "Freq1")
blmm_target_SFD_exp2_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp2_gaussian, "Tracker1")
blmm_target_SFD_exp2_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp2_gaussian, "Freq1:Tracker1")

blmm_target_TVT_exp2_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp2_gaussian, "Freq1")
blmm_target_TVT_exp2_gaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp2_gaussian, "Tracker1")
blmm_target_TVT_exp2_gaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp2_gaussian, "Freq1:Tracker1")

# estimated marginal means: low - high within each tracker
marginal_effects_exp2_target_FFD <- emmeans(blmm_target_FFD_exp2_gaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_target_GD <- emmeans(blmm_target_GD_exp2_gaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_target_SFD <- emmeans(blmm_target_SFD_exp2_gaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_target_TVT <- emmeans(blmm_target_TVT_exp2_gaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_string_exp2_target_FFD <- format_contrast_string(marginal_effects_exp2_target_FFD)
marginal_effects_string_exp2_target_SFD <- format_contrast_string(marginal_effects_exp2_target_SFD)
marginal_effects_string_exp2_target_GD <- format_contrast_string(marginal_effects_exp2_target_GD)
marginal_effects_string_exp2_target_TVT <- format_contrast_string(marginal_effects_exp2_target_TVT)
```

```{r}
#| label: tbl-exp2-target-word-means
#| echo: false
#| message: false
#| after-caption-space: 0pt
#| tbl-cap: "Mean first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 2 by eye-tracker and word frequency condition."
#| cache: true

target_words_exp2_means_table <- target_words_exp2 %>% 
  group_by(Tracker, Freq) %>%
  summarise(
    mean_FFD = mean(FFD, na.rm = TRUE),
    sd_FFD = sd(FFD, na.rm = TRUE),
    mean_SFD = mean(SFD, na.rm = TRUE),
    sd_SFD = sd(SFD, na.rm = TRUE),
    mean_GD = mean(GD, na.rm = TRUE),
    sd_GD = sd(GD, na.rm = TRUE),
    mean_TVT = mean(TVT, na.rm = TRUE),
    sd_TVT = sd(TVT, na.rm = TRUE),
  ) %>%
  ungroup()

target_words_exp2_means_table %>%
  gt(rowname_col = "Tracker") %>%
  cols_label(
   starts_with("mean") ~ "Mean",
   starts_with("sd") ~ "SD",
   "Freq" ~ "Frequency"
  ) %>%
  tab_spanner(label = "FFD", columns = ends_with("FFD")) %>%
  tab_spanner(label = "SFD", columns = ends_with("SFD")) %>%
  tab_spanner(label = "GD", columns = ends_with("GD")) %>%
  tab_spanner(label = "TVT", columns = ends_with("TVT")) %>%
  fmt_number(columns = everything(), decimals = 0) %>%
  tab_stubhead(label = "Tracker") %>%
  tab_source_note(source_note = md("Note: *FFD* = first fixation duration; *SFD* = single fixation duration; *GD* = gaze duration; *TVT* = total viewing time; SD = standard deviation. All means and standard deviations are reported in milliseconds (ms)."))
```

#### Target word analysis

@tbl-exp2-target-word-means shows the means and standard deviations for the four fixation time measures on target words in Experiment 2, while @tbl-eyelink-exp2-target-word-brms-modelsummary shows the corresponding model estimates.

```{r}
#| label: tbl-eyelink-exp2-target-word-brms-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 2."

coef_map <- c("b_Intercept" = "Intercept",
              "b_Freq1" = "Frequency",
              "b_Tracker1" = "Tracker",
              "b_Freq1:Tracker1" = "Frequency × Tracker")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_target_FFD_exp2_gaussian, SFD = blmm_target_SFD_exp2_gaussian, GD = blmm_target_GD_exp2_gaussian, TVT = blmm_target_TVT_exp2_gaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

As in Experiment 1, we observed a frequency effect in the expected direction across both devices: low-frequency words elicited longer fixations than high-frequency words (FFD: `r blmm_target_FFD_exp2_gaussian_mu_Freq1_effect`; SFD: `r blmm_target_SFD_exp2_gaussian_mu_Freq1_effect`; GD: `r blmm_target_GD_exp2_gaussian_mu_Freq1_effect`; TVT: `r blmm_target_TVT_exp2_gaussian_mu_Freq1_effect`). 
Fixation times were again longer with the Webcam than with the Eyelink (FFD: `r blmm_target_FFD_exp2_gaussian_mu_Tracker1_effect`; SFD: `r blmm_target_SFD_exp2_gaussian_mu_Tracker1_effect`; GD: `r blmm_target_GD_exp2_gaussian_mu_Tracker1_effect`; TVT: `r blmm_target_TVT_exp2_gaussian_mu_Tracker1_effect`).
Again, we did not see a credible Frequency × Tracker interaction (FFD: `r blmm_target_FFD_exp2_gaussian_mu_interaction_effect`; SFD: `r blmm_target_SFD_exp2_gaussian_mu_interaction_effect`; GD: `r blmm_target_GD_exp2_gaussian_mu_interaction_effect`; TVT: `r blmm_target_TVT_exp2_gaussian_mu_interaction_effect`).

Again as in Experiment 1, we summarized the low–high frequency contrast separately within each device using estimated marginal means. Interestingly, in Experiment 2, the Webcam data actually contained stronger evidence in favor of the frequency effect than the Eyelink data, with the 95% CI for the frequency effect excluding 0 for both devices in FFD (`r marginal_effects_string_exp2_target_FFD`) and GD (`r marginal_effects_string_exp2_target_GD`), although the exclusion was very narrow for the Eyelink data), but only for the Webcam data in SFD (`r marginal_effects_string_exp2_target_SFD`) and TVT (`r marginal_effects_string_exp2_target_TVT`). These somewhat unexpected results show that the Webcam data, although noisier, do not necessarily always underestimate the size of an effect. In any case, our results highlight that a large number of observations are needed to detect even strong effects such as the word frequency effect reliably at a sampling rate of 30 Hz (as suggested by Angele et al., 2025).

#### Corpus-style analysis

```{r}
#| label: load-exp2-corpus-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the Gaussian corpus models
blmm_corpus_FFD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_FFD_exp2_gaussian.qs"))
blmm_corpus_SFD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_SFD_exp2_gaussian.qs"))
blmm_corpus_GD_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_GD_exp2_gaussian.qs"))
blmm_corpus_TVT_exp2_gaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_TVT_exp2_gaussian.qs"))

# emtrends for frequency slopes by tracker
marginal_effects_exp2_corpus_FFD <- emtrends(blmm_corpus_FFD_exp2_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_corpus_GD <- emtrends(blmm_corpus_GD_exp2_gaussian, "Tracker", "zipf")  %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_corpus_SFD <- emtrends(blmm_corpus_SFD_exp2_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp2_corpus_TVT <- emtrends(blmm_corpus_TVT_exp2_gaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_string_exp2_corpus_FFD <- format_contrast_string(marginal_effects_exp2_corpus_FFD)
marginal_effects_string_exp2_corpus_GD <- format_contrast_string(marginal_effects_exp2_corpus_GD)
marginal_effects_string_exp2_corpus_SFD <- format_contrast_string(marginal_effects_exp2_corpus_SFD)
marginal_effects_string_exp2_corpus_TVT <- format_contrast_string(marginal_effects_exp2_corpus_TVT)
```

```{r}
#| label: tbl-exp2-corpus-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: false
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on all words (except for the first and last in each sentence) in Experiment 2."

coef_map_corpus <- c("b_Intercept" = "Intercept",
              "b_ctrzipf" = "Zipf frequency",
              "b_Tracker1" = "Tracker",
              "b_ctrzipf:Tracker1" = "Frequency × Tracker")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_corpus_FFD_exp2_gaussian, SFD = blmm_corpus_SFD_exp2_gaussian, GD = blmm_corpus_GD_exp2_gaussian, TVT = blmm_corpus_TVT_exp2_gaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map_corpus,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

For Experiment 2, we also fit models predicting fixation times on all the words in every sentence (except for sentence-initial and sentence-final words), with Zipf frequency as a continuous predictor and tracker as a discrete factor with two levels, Eyelink and Webcam, as was done for the Experiment 1 data. @tbl-exp2-corpus-modelsummary summarizes the Zipf frequency effect, the effect of the tracker used, and their interaction over all eligible words. We again observed a frequency effect, with higher frequency words being associated with shorter fixations, but this effect was much stronger in Experiment 2 (FFD: `r brms_effect_summary(blmm_corpus_FFD_exp2_gaussian, "ctrzipf")`; SFD: `r brms_effect_summary(blmm_corpus_SFD_exp2_gaussian, "ctrzipf")`; GD: `r brms_effect_summary(blmm_corpus_GD_exp2_gaussian, "ctrzipf")`; TVT: `r brms_effect_summary(blmm_corpus_TVT_exp2_gaussian, "ctrzipf")`). Just as we had observed in all the previous analyses, the Webcam data resulted in longer detected fixations overall (FFD: `r brms_effect_summary(blmm_corpus_FFD_exp2_gaussian, "Tracker1")`; SFD: `r brms_effect_summary(blmm_corpus_SFD_exp2_gaussian, "Tracker1")`; GD: `r brms_effect_summary(blmm_corpus_GD_exp2_gaussian, "Tracker1")`; TVT: `r brms_effect_summary(blmm_corpus_TVT_exp2_gaussian, "Tracker1")`). There was no credible evidence for an interaction between Zipf frequency and tracker in FFD (`r brms_effect_summary(blmm_corpus_FFD_exp2_gaussian, "ctrzipf:Tracker1")`), but there was a credible interaction in SFD (`r brms_effect_summary(blmm_corpus_SFD_exp2_gaussian, "ctrzipf:Tracker1")`), GD (`r brms_effect_summary(blmm_corpus_GD_exp2_gaussian, "ctrzipf:Tracker1")`), and TVT (`r brms_effect_summary(blmm_corpus_TVT_exp2_gaussian, "ctrzipf:Tracker1")`). Importantly, the direction of this interaction was opposite to those observed in Experiment 1: Just as in the target word analysis, the frequency effect was stronger in the Webcam data compared to the Eyelink data. Finally, we again report `emtrends` estimates and 95% CIs for Eyelink and Webcam data separately. Unlike in Experiment 1, the frequency effect was credible for both the Eyelink and the Webcam data in all measures (FFD: `r marginal_effects_string_exp2_corpus_FFD`; SFD: `r marginal_effects_string_exp2_corpus_SFD`; GD: `r marginal_effects_string_exp2_corpus_GD`; TVT `r marginal_effects_string_exp2_corpus_TVT`). This may be due to the higher number of observations in Experiment 2.

## Experiment 3

### Method

#### Participants

#### Measures

#### Procedure

#### Data analysis

The model specifications and data analysis were the same as in Experiment 1, except that Tracker was not included as a predictor since all data were collected remotely using the Webcam.

#### Results

#### Target word analysis

```{r}
#| label: load-exp3-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the fixation time measures
target_words_exp3 <- read_csv(here("Prolific/data/target_word_frequency_dat.csv")) %>%
  mutate(Freq = factor(Freq, levels = c("low", "high")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp3 <- read_csv(here("Prolific/data/corpus_fixation_data.csv")) %>%
  mutate(item = factor(item),
         sub = factor(sub))

# load the Gaussian model results
blmm_target_FFD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_target_FFD_exp3_gaussian.qs"))
blmm_target_SFD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_target_SFD_exp3_gaussian.qs"))
blmm_target_GD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_target_GD_exp3_gaussian.qs"))
blmm_target_TVT_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_target_TVT_exp3_gaussian.qs"))

# prepare effect summaries 
blmm_target_FFD_exp3_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp3_gaussian, "Freq1")

blmm_target_GD_exp3_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp3_gaussian, "Freq1")


blmm_target_SFD_exp3_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp3_gaussian, "Freq1")

blmm_target_TVT_exp3_gaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp3_gaussian, "Freq1")


# estimated marginal means: low - high within each tracker
format_contrast_string <- function(data) {
  tracker_strings <- data %>%
    mutate(
      report_string = sprintf(
        "%s: *M* = %.2f 95%% *CI* = [%.2f, %.2f]",
        Tracker,
        .value,
        .lower,
        .upper
      )
    ) %>%
    pull(report_string)
  sprintf("%s", str_c(tracker_strings, collapse = "; "))
}

```

```{r}
#| label: tbl-exp3-target-word-means
#| echo: false
#| message: false
#| after-caption-space: 0pt
#| tbl-cap: "Mean first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1 by eye-tracker and word frequency condition."

target_words_exp3_means_table <- target_words_exp3 %>%
  group_by(Freq) %>%
  summarise(
    mean_FFD = mean(FFD, na.rm = TRUE),
    sd_FFD = sd(FFD, na.rm = TRUE),
    mean_SFD = mean(SFD, na.rm = TRUE),
    sd_SFD = sd(SFD, na.rm = TRUE),
    mean_GD = mean(GD, na.rm = TRUE),
    sd_GD = sd(GD, na.rm = TRUE),
    mean_TVT = mean(TVT, na.rm = TRUE),
    sd_TVT = sd(TVT, na.rm = TRUE),
  ) %>%
  ungroup()

target_words_exp3_means_table %>%
  gt() %>%
  cols_label(
   starts_with("mean") ~ "Mean",
   starts_with("sd") ~ "SD",
   "Freq" ~ "Frequency"
  ) %>%
  tab_spanner(label = "FFD", columns = ends_with("FFD")) %>%
  tab_spanner(label = "SFD", columns = ends_with("SFD")) %>%
  tab_spanner(label = "GD", columns = ends_with("GD")) %>%
  tab_spanner(label = "TVT", columns = ends_with("TVT")) %>%
  fmt_number(columns = everything(), decimals = 0) %>%
  tab_stubhead(label = "Tracker") %>%
  tab_source_note(source_note = md("Note: *FFD* = first fixation duration; *SFD* = single fixation duration; *GD* = gaze duration; *TVT* = total viewing time; SD = standard deviation. All means and standard deviations are reported in milliseconds (ms)."))
```

@tbl-exp3-target-word-means shows the mean and standard deviation of first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 3 by word frequency condition, while @tbl-exp3-target-modelsummary shows the model estimates.

```{r}
#| label: tbl-exp3-target-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 3."

# can use the same coef_map even though we don't have Tracker in this model
coef_map <- c("b_Intercept" = "Intercept",
              "b_Freq1" = "Frequency",
              "b_Tracker1" = "Tracker",
              "b_Freq1:Tracker1" = "Frequency × Tracker")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_target_FFD_exp3_gaussian, SFD = blmm_target_SFD_exp3_gaussian, GD = blmm_target_GD_exp3_gaussian, TVT = blmm_target_TVT_exp3_gaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

In Experiment 3, low-frequency target words elicited longer fixation times than high-frequency target words in SFD (`r blmm_target_SFD_exp3_gaussian_mu_Freq1_effect`), GD (`r blmm_target_GD_exp3_gaussian_mu_Freq1_effect`), and TVT (`r blmm_target_TVT_exp3_gaussian_mu_Freq1_effect`). In FFD, the CI narrowly included 0 (`r blmm_target_FFD_exp3_gaussian_mu_Freq1_effect`). Overall, this demonstrates that, despite the much lower control we had over devices and experimental setup in the online study, reliable word frequency effects could be found.

#### Corpus-style analysis

As in Experiment 1, we also fitted Bayesian linear mixed models including all words in every sentence (both the multi-line sentences with the frequency manipulation and the single-line sentences) into the analysis. This increased the number of observations substantially compared to the target word analysis.

@tbl-exp3-corpus-modelsummary shows the results of these "corpus-analysis style" Bayesian linear mixed models with Zipf frequency as a continuous predictor for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT) on all words in the sentences (except for the first and last word in each sentence) in Experiment 3.  

```{r}
#| label: load-exp3-corpus-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the Gaussian corpus model results

blmm_corpus_FFD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_corpus_FFD_exp3_gaussian.qs"))
blmm_corpus_SFD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_corpus_SFD_exp3_gaussian.qs"))
blmm_corpus_GD_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_corpus_GD_exp3_gaussian.qs"))
blmm_corpus_TVT_exp3_gaussian <- qs_read(here("Prolific", "models", "brms", "blmm_corpus_TVT_exp3_gaussian.qs"))
```

```{r}
#| label: tbl-exp3-corpus-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on all words (except for the first and last in each sentence) in Experiment 3."

coef_map_corpus <- c("b_Intercept" = "Intercept",
              "b_ctrzipf" = "Zipf frequency")

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"
stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_corpus_FFD_exp3_gaussian, SFD = blmm_corpus_SFD_exp3_gaussian, GD = blmm_corpus_GD_exp3_gaussian, TVT = blmm_corpus_TVT_exp3_gaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map_corpus,
             gof_map = NA,
             output = "gt") |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

In Experiment 3, we observed a consistent effect of zipf frequency on all measures (FFD: `r brms_effect_summary(blmm_corpus_FFD_exp3_gaussian, "ctrzipf")`; SFD: `r brms_effect_summary(blmm_corpus_SFD_exp3_gaussian, "ctrzipf")`; GD: `r brms_effect_summary(blmm_corpus_GD_exp3_gaussian, "ctrzipf")`; TVT: `r brms_effect_summary(blmm_corpus_TVT_exp3_gaussian, "ctrzipf")`). This again demonstrates that, when there is a sufficiently high number of observations, the frequency effect can be detected  using online Webcam eye tracking where we do not have direct control over the experimental setup.

# Discussion

## Limitations and Future Directions

## Conclusion

# References

::: {#refs}
:::

# This Section Is an Appendix {#apx-a}

# Another Appendix {#apx-b}
