---
title: "Webcam analysis"
shorttitle: "Webcam analysis"
author:
  - name: First Author
    corresponding: true
    orcid: 0000-0000-0000-0001
    email: janedoe@generic.edu
    affiliations:
      - name: Generic University
        department: Department
        address: 1234 Capital St.
        city: New York
        region: NY
        country: USA
        postal-code: 12084-1234
author-note:
  status-changes: 
    affiliation-change: null
    deceased: null
  disclosures:
    study-registration: null
    data-sharing: null
    related-report: null
    conflict-of-interest: null
    financial-support: null
    gratitude: null
    authorship-agreements: null
abstract: "This document is a template."
impact-statement: "This template helps you get started."
keywords: [Keyword 1, Keyword 2, Keyword 3]
bibliography: bibliography.bib
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-typst: default
  apaquarto-pdf:
    documentmode: man
editor_options: 
  chunk_output_type: inline
---

```{r}
#| label: setup
#| include: false
library(conflicted)
library(tidyverse)
library(dplyr)
library(qs2)
library(gt)
library(gtsummary)
library(flextable)
library(ftExtra)
library(knitr)
library(kableExtra)
library(here)
library(simr)
# we only use papaja here for the R package citation functions (r_refs and cite_r)
library(papaja)
library(tidybayes)
library(marginaleffects)
library(emmeans)
conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(dplyr::select, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)

ctr <- function(x) scale(x, scale = FALSE)

source("brms_effect_summary.R")
#r_refs("r-references.bib")

# do we still need these functions?

# convenience function to format descriptive summary statistics as "mean (sd)"
print_mean_sd <- function(datum, digits_mean = 0, digits_sd = 2){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)) %>% format_value(digits = digits_sd)})")
}

# convenience function to format inferential summary statistics as "mean (se)"
print_mean_se <- function(datum, digits_mean = 0, digits_se = 2){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)/sqrt(length(datum))) %>% format_value(digits = digits_se)})")
}

# convenience function to format range summary statistics as "min -- max"
print_range <- function(datum, digits_min = 2, digits_max = 2){
  str_glue("({min(datum) %>% format_value(digits = digits_min)} -- {max(datum) %>% format_value(digits = digits_max)})")
}

print_mean_sd_range <- function(datum, digits_mean = 2, digits_sd = 2, digits_min = 0, digits_max = 0){
  str_glue("{mean(datum) %>% format_value(digits = digits_mean)} ({(sd(datum)) %>% format_value(digits = digits_sd)}; {min(datum) %>% format_value(digits = digits_min)} -- {max(datum) %>% format_value(digits = digits_max)})")
}

# format value for in-text statistics
format_value <- function(value) {
    if (is.na(value) || !is.numeric(value)) {
      return(as.character(value))
    }
    # For numbers with small magnitude (but not zero), show significant digits
    if (abs(value) < 0.01 && value != 0) {
      # formatC with 'g' and digits=2 prints in a nice format, e.g., 0.0034
      # signif() could also be used, but formatC is robust.
      return(formatC(value, format = "g", digits = 2))
    } else {
      # For numbers >= 0.01 or exactly 0, round to 2 decimal places
      return(format(round(value, 2), nsmall = 2))
    }
  }

make_gtsummary_table_for_target_word_brm <- function(brmsfit) {
  tbl_regression(brmsfit, exponentiate = FALSE, intercept = TRUE,label = list(`Freq` ~ "Frequency", `Tracker` ~ "Eye tracker", `factor(Freq):factor(Tracker(` ~ "Interaction"), show_single_row = any_of(c("Freq", "Tracker")),
                 estimate_fun = ~style_sigfig(., digits = 3)) %>%
    modify_table_styling(
      columns = c(estimate, conf.low), # use `show_header_names()` to see underlying column names
      rows = !(0 >= conf.low & 0 <= conf.high), #CrI does not include 0
      text_format = "bold") %>%
    modify_header(label = "**Variable**", estimate = "**b**", conf.low = "**CrI**") %>%
    modify_abbreviation("CrI = 95% Credible Interval") %>%
    remove_abbreviation("CI = Credible Interval")
}

library(sjPlot)


library(modelsummary)


```

<!-- The introduction should not have a level-1 heading such as Introduction. -->

This is my first paragraph. Any section headings in the introduction should be in levels 2--5.

## Section in Introduction

This is a reference [@cohen2003applied].

## Experiment 1

### Method

### Participants

### Measures

### Procedure

### Data analysis

We analysed the data for the frequency corpus by fitting Bayesian linear mixed models using the *brms* package [@R-brms_a; @R-brms_b; @R-brms_c] in R^[The versions of R and all packages used are as follows: `r #papaja::cite_r("r-references.bib")`.]. These models included the word frequency condition (low, represented as -.5, vs. high, represented as .5) as well as the eye-tracker used (with the Eyelink represented as -.5 and the Webcam represented as .5). We included the maximum random effects structure [i.e., random intercepts and random slopes for condition, stimulus type, and their interaction over subjects and random intercepts and random slopes for condition over items, @barr2013]. We used the ex-Gaussian distribution to model fixation times, after excluding excessively short (\< 80 ms) and long observations (first fixation duration and single fixation duration \> 1,000 ms; gaze duration > 1,800 ms; total viewing time > 2,000), with both the mean of the Gaussian component $\mu_{RT}$ and the scale parameter of the exponential component $\beta_{RT}$ (equaling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions. We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $b \sim N(0,250)$ for the coefficients related to $\mu$ and  $b \sim N(0,1)$ for the coefficients related to $\beta$ in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations. The models converged successfully (all $\hat{R}$s = 1.00). We report the mean, the estimates (b) and the 95% Bayesian Credible Intervals (95% CrIs) based on the posterior distribution of each model parameter. In order to simplify the interpretation of the posterior distribution, we highlight whether 0 is not a credible value for its coefficient (i.e., if it is not part of the 95% CrI). Additionally, we report the proportion of the posterior distribution on the same side of 0 (i.e., the proportion of the posterior distribution that is greater than 0 or less than 0). We always report the greater proportion (e.g., if 49% of the posterior distribution is \< 0 and 51 % is \> 0 we report .51). We also report the ratio of the two proportions (with the greater proportion always in the numerator), which effectively corresponds to a Bayes Factor for the directional hypothesis b \> 0 or b \< 0, respectively. Finally, we report the Bayes Factor (BF) calculated using the Savage-Dickey density ratio which tests the evidence for the point-null hypothesis b = 0. These measures all provide complementary information about the effect in question. We interpret BF values of 3-10 as moderate evidence, 10-30 as strong evidence, and \>30 as very strong evidence for the effect [@jeffreys1961].

### Results

#### Target word analysis

```{r}
#| label: load-exp1-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the fixation time measures
target_words_exp1 <- read_csv(here("LAB/data/target_word_fixation_data.csv")) %>%
  mutate(Freq = factor(Freq, levels = c("low", "high")),
         Tracker = factor(Tracker, levels = c("Webcam", "Eyelink")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp1 <- read_csv(here("LAB/data/corpus_fixation_data.csv")) %>%
  mutate(Tracker = factor(Tracker, levels = c("Eyelink", "Webcam")),
         item = factor(item),
         sub = factor(sub))



# load the model results
blmm_target_FFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_FFD_exp1_gaussian.qs"))
blmm_target_SFD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_SFD_exp1_gaussian.qs"))
blmm_target_GD_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_GD_exp1_gaussian.qs"))
blmm_target_TVT_exp1_gaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_TVT_exp1_gaussian.qs"))

blmm_target_FFD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_FFD_exp1_exgaussian.qs"))
blmm_target_SFD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_SFD_exp1_exgaussian.qs"))
blmm_target_GD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_GD_exp1_exgaussian.qs"))
blmm_target_TVT_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_target_TVT_exp1_exgaussian.qs"))


# prepare effect summaries
blmm_target_FFD_exp1_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "Freq1")
blmm_target_FFD_exp1_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "Tracker1")
blmm_target_FFD_exp1_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "Freq1:Tracker1")

blmm_target_FFD_exp1_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "beta_Freq1")
blmm_target_FFD_exp1_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "beta_Tracker1")
blmm_target_FFD_exp1_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp1_exgaussian, "beta_Freq1:Tracker1")

blmm_target_GD_exp1_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "Freq1")
blmm_target_GD_exp1_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "Tracker1")
blmm_target_GD_exp1_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "Freq1:Tracker1")

blmm_target_GD_exp1_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "beta_Freq1")
blmm_target_GD_exp1_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "beta_Tracker1")
blmm_target_GD_exp1_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_GD_exp1_exgaussian, "beta_Freq1:Tracker1")

blmm_target_SFD_exp1_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "Freq1")
blmm_target_SFD_exp1_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "Tracker1")
blmm_target_SFD_exp1_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "Freq1:Tracker1")
                                                                             
blmm_target_SFD_exp1_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "beta_Freq1")
blmm_target_SFD_exp1_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "beta_Tracker1")
blmm_target_SFD_exp1_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp1_exgaussian, "beta_Freq1:Tracker1")

blmm_target_TVT_exp1_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "Freq1")
blmm_target_TVT_exp1_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "Tracker1")
blmm_target_TVT_exp1_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "Freq1:Tracker1")

blmm_target_TVT_exp1_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "beta_Freq1")
blmm_target_TVT_exp1_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "beta_Tracker1")
blmm_target_TVT_exp1_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp1_exgaussian, "beta_Freq1:Tracker1")


# save emmeans values. Use gather_emmeans_draws and mean_qi to get credible intervals instead of HPD (https://discourse.mc-stan.org/t/emmeans-or-hypothesis-for-getting-comparisons-with-mixed-model-for-repeated-measures-mmrm-fitted-with-brms/29831)

marginal_effects_exp1_target_FFD <- emmeans(blmm_target_FFD_exp1_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp1_target_GD <- emmeans(blmm_target_GD_exp1_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp1_target_SFD <- emmeans(blmm_target_SFD_exp1_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp1_target_TVT <- emmeans(blmm_target_TVT_exp1_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

# format these for inclusion in the text

format_contrast_string <- function(data) {

  # Create the individual string components for each tracker
  # Using sprintf() to format numbers to two decimal places
  tracker_strings <- data %>%
    mutate(
      report_string = sprintf(
        "%s: *M* = %.2f 95%% *CI* = [%.2f, %.2f]",
        Tracker,
        .value,
        .lower,
        .upper
      )
    ) %>%
    # Pull the formatted strings into a vector
    pull(report_string)

  # Join all tracker strings together, separated by a semicolon and space
  combined_string <- str_c(tracker_strings, collapse = "; ")

  # Wrap the final string in parentheses
  final_string <- sprintf("(%s)", combined_string)

  return(final_string)
}

marginal_effects_string_exp1_target_FFD <- format_contrast_string(marginal_effects_exp1_target_FFD)
marginal_effects_string_exp1_target_SFD <- format_contrast_string(marginal_effects_exp1_target_SFD)
marginal_effects_string_exp1_target_GD <- format_contrast_string(marginal_effects_exp1_target_GD)
marginal_effects_string_exp1_target_TVT <- format_contrast_string(marginal_effects_exp1_target_TVT)


```


```{r}
#| label: tbl-exp1-target-word-means
#| echo: false
#| message: false
#| after-caption-space: 0pt
#| tbl-cap: "Mean first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1 by eye-tracker and word frequency condition."

# Calculate means and standard deviations for target word fixation time measures
target_words_exp1_means_table <- target_words_exp1 %>%
  #filter(FFD > 80 & FFD < 1500) %>%
  group_by(Tracker, Freq) %>%
  summarise(
    mean_FFD = mean(FFD, na.rm = TRUE),
    sd_FFD = sd(FFD, na.rm = TRUE),
    mean_SFD = mean(SFD, na.rm = TRUE),
    sd_SFD = sd(SFD, na.rm = TRUE),
    mean_GD = mean(GD, na.rm = TRUE),
    sd_GD = sd(GD, na.rm = TRUE),
    mean_TVT = mean(TVT, na.rm = TRUE),
    sd_TVT = sd(TVT, na.rm = TRUE),
    #N = n() # N here is the number of correct trials within the RT filter
  ) %>%
  ungroup()

# use gt to make a table

target_words_exp1_means_table %>%
  gt(rowname_col = "Tracker") %>%
  cols_label(
   starts_with("mean") ~ "Mean",
   starts_with("sd") ~ "SD",
   "Freq" ~ "Frequency"
  ) %>%
  tab_spanner( # Add spanner columns for fixation time measures
    label = "FFD",
    columns = ends_with("FFD")
  ) %>%
  tab_spanner(
    label = "SFD",
    columns = ends_with("SFD")
  ) %>%
  tab_spanner(
    label = "GD",
    columns = ends_with("GD")
  ) %>%
  tab_spanner(
    label = "TVT",
    columns = ends_with("TVT")
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 0
  ) %>%
  tab_stubhead(label = "Tracker") %>%
  tab_source_note(source_note = md("Note: *FFD* = first fixation duration; *SFD* = single fixation duration; *GD* = gaze duration; *TVT* = total viewing time; SD = standard deviation. All means and standard deviations are reported in milliseconds (ms)."))
                
```


@tbl-exp1-target-word-means shows the mean and standard deviation of first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1 by eye-tracker and word frequency condition, while @tbl-eyelink-exp1-target-word-brms-modelsummary shows the results of the Bayesian linear mixed model for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT).

```{r}
#| label: tbl-exp1-target-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 1."


coef_map <- c("b_Intercept" = "Intercept (μ)",
              "b_Freq1" = "Frequency (μ)",
              "b_Tracker1" = "Tracker (μ)",
              "b_Freq1:Tracker1" = "Frequency × Tracker (μ)",
              "b_beta_Intercept" = "Intercept (β)",
              "b_beta_Freq1" = "Frequency (β)",
              "b_beta_Tracker1" = "Tracker (β)",
              "b_beta_Freq1:Tracker1" = "Frequency × Tracker (β)")

# Pass the map to the coef_map argument

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"

stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_target_FFD_exp1_exgaussian, SFD = blmm_target_SFD_exp1_exgaussian, GD = blmm_target_GD_exp1_exgaussian, TVT = blmm_target_TVT_exp1_exgaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map,
             gof_map = NA,
             output = "gt",
  
) |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))


```
In all fixation time measures, there was a main effect of word frequency on the Gaussian component $\mu$, such that low-frequency words elicited longer fixation times than high-frequency words (FFD: `r blmm_target_FFD_exp1_exgaussian_mu_Freq1_effect`; SFD: `r blmm_target_SFD_exp1_exgaussian_mu_Freq1_effect`; GD: `r blmm_target_GD_exp1_exgaussian_mu_Freq1_effect`; TVT: `r blmm_target_TVT_exp1_exgaussian_mu_Freq1_effect`). There was also a main effect of eye-tracker, such that fixation times were longer when recorded with the Webcam compared to the Eyelink (FFD: `r blmm_target_FFD_exp1_exgaussian_mu_Tracker1_effect`; SFD: `r blmm_target_SFD_exp1_exgaussian_mu_Tracker1_effect`; GD: `r blmm_target_GD_exp1_exgaussian_mu_Tracker1_effect`; TVT: `r blmm_target_TVT_exp1_exgaussian_mu_Tracker1_effect`). Importantly, there was no credible interaction between word frequency and eye-tracker in any of the fixation time measures (FFD: `r blmm_target_FFD_exp1_exgaussian_mu_interaction_effect`; SFD: `r blmm_target_SFD_exp1_exgaussian_mu_interaction_effect`; GD: `r blmm_target_GD_exp1_exgaussian_mu_interaction_effect`; TVT: `r blmm_target_TVT_exp1_exgaussian_mu_interaction_effect`), suggesting that Eyelink data and Webcam data both showed a frequency effect.
On the scale component $\beta$, we observed a credible effect of word frequency on FFD (`r blmm_target_FFD_exp1_exgaussian_beta_Freq1_effect`), GD (`r blmm_target_GD_exp1_exgaussian_beta_Freq1_effect`), and TVT (`r blmm_target_TVT_exp1_exgaussian_beta_Freq1_effect`), indicating that the posterior distribution of fixation times for low-frequency words had a longer right tail than that for high-frequency words.
There was a very strong effect of eye-tracker on the scale component in FFD (`r blmm_target_FFD_exp1_exgaussian_beta_Tracker1_effect`), SFD (`r blmm_target_SFD_exp1_exgaussian_beta_Tracker1_effect`), GD (`r blmm_target_GD_exp1_exgaussian_beta_Tracker1_effect`), and TVT (`r blmm_target_TVT_exp1_exgaussian_beta_Tracker1_effect`), indicating that the posterior distribution of fixation times recorded with the Webcam had a longer right tail than that recorded with the Eyelink. This is likely due to a systematic difference in the saccade and fixation detection algorithms.

There were no credible interactions between word frequency and eye-tracker on the scale component any of the fixation time measures except for gaze duration (FFD: `r blmm_target_FFD_exp1_exgaussian_beta_interaction_effect`; SFD: `r blmm_target_SFD_exp1_exgaussian_beta_interaction_effect`; GD: `r blmm_target_GD_exp1_exgaussian_beta_interaction_effect`; TVT: `r blmm_target_TVT_exp1_exgaussian_beta_interaction_effect`). The interaction in gaze duration indicates that the longer tail for low frequency words was mainly observed on the Eyelink, not the Webcam.

The absence of an interaction between frequency and tracker is not positive evidence for a frequency effect in the Webcam data on its own. We calculated posterior distributions for the estimated marginal means of the difference between low and high frequency target words and found that the 95% credible intervals for these differences in the Webcam data included 0 in all fixation time measures, while the credible intervals for the Eyelink data excluded 0 in all the fixation time measures except for TVT (FFD: `r marginal_effects_string_exp1_target_FFD`; SFD: `r marginal_effects_string_exp1_target_SFD`; GD: `r marginal_effects_string_exp1_target_GD`; TVT: `r marginal_effects_string_exp1_target_TVT`), indicating that, while the effect estimate was in the same direction across the two trackers, there was not enough evidence in the Experiment 1 webcam data to conclusively determine that a frequency effect was present.


#### Corpus-style analysis

@tbl-exp1-corpus-modelsummary shows the results of the corpus-style Bayesian linear mixed models for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT) on all words in the sentences (except for the first and last word in each sentence) in Experiment 1.

```{r}
#| label: load-exp1-corpus-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the model results

blmm_corpus_FFD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_FFD_exp1_exgaussian.qs"))
blmm_corpus_SFD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_SFD_exp1_exgaussian.qs"))
blmm_corpus_GD_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_GD_exp1_exgaussian.qs"))
blmm_corpus_TVT_exp1_exgaussian <- qs_read(here("LAB", "models", "brms", "blmm_corpus_TVT_exp1_exgaussian.qs"))

# prepare effect summaries
blmm_corpus_FFD_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_FFD_exp1_exgaussian, "ctrzipf")
blmm_corpus_FFD_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_FFD_exp1_exgaussian, "Tracker1")
blmm_corpus_FFD_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_SFD_exp1_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_SFD_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_SFD_exp1_exgaussian, "ctrzipf")
blmm_corpus_SFD_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_SFD_exp1_exgaussian, "Tracker1")
blmm_corpus_SFD_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_SFD_exp1_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_GD_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "ctrzipf")
blmm_corpus_GD_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "Tracker1")
blmm_corpus_GD_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_TVT_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "ctrzipf")
blmm_corpus_TVT_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "Tracker1")
blmm_corpus_TVT_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "ctrzipf:Tracker1")

# save emmeans calculations for testing the marginal effect of frequency by tracker

marginal_effects_exp1_corpus_FFD <- emtrends(blmm_corpus_FFD_exp1_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_GD <- emtrends(blmm_corpus_GD_exp1_exgaussian, "Tracker", "zipf")  %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_SFD <- emtrends(blmm_corpus_SFD_exp1_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp1_corpus_TVT <- emtrends(blmm_corpus_TVT_exp1_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

```

```{r}
#| label: tbl-exp1-corpus-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on all words (except for the first and last in each sentence) in Experiment 1."

coef_map_corpus <- c("b_Intercept" = "Intercept (μ)",
              "b_ctrzipf" = "Zipf frequency (μ)",
              "b_Tracker1" = "Tracker (μ)",
              "b_ctrzipf:Tracker1" = "Frequency × Tracker (μ)",
              "b_beta_Intercept" = "Intercept (β)",
              "b_beta_ctrzipf" = "Zipf frequency (β)",
              "b_beta_Tracker1" = "Tracker (β)",
              "b_beta_ctrzipf:Tracker1" = "Frequency × Tracker (β)")

# Pass the map to the coef_map argument

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"

stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_corpus_FFD_exp1_exgaussian, SFD = blmm_corpus_SFD_exp1_exgaussian, GD = blmm_corpus_GD_exp1_exgaussian, TVT = blmm_corpus_TVT_exp1_exgaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map_corpus,
             gof_map = NA,
             output = "gt",
  
) |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))
```

## Experiment 3

### Method

#### Participants

#### Measures

#### Procedure

#### Data analysis

The model specifications and data analysis were the same as in Experiment 1.


### Results

```{r}
#| label: load-exp3-target-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the fixation time measures
target_words_exp3 <- read_csv(here("LAB-SPAIN/data/target_word_fixation_data.csv")) %>%
  mutate(Freq = factor(Freq, levels = c("low", "high")),
         Tracker = factor(Tracker, levels = c("Webcam", "Eyelink")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp3 <- read_csv(here("LAB-SPAIN/data/all_words_fixation_data.csv")) %>%
  mutate(Tracker = factor(Tracker, levels = c("Eyelink", "Webcam")),
         item = factor(item),
         sub = factor(sub))

corpus_words_exp3 <- corpus_words_exp3 %>% 
  mutate(position = case_when(grepl("\\.$", wordID) & word_num == max(word_num) ~ "last", 
                              word_num == 1 ~ "first", 
                              TRUE ~ "middle"),
# make a word code uniquely identifying each word, combining item and word_num
word_code = paste(item, word_num, sep = "_"), len = nchar(wordID))

exp3_word_frequency_data <- read_tsv(here("LAB-SPAIN/spanish_corpus_words_with_frequencies_espal.txt")) %>% select(word,frq,zipf,num_letters)

corpus_words_exp3 <- corpus_words_exp3 %>%
  left_join(exp3_word_frequency_data, by = c("wordID" = "word"))




# load the model results
blmm_target_FFD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_FFD_exp3_exgaussian.qs"))
blmm_target_SFD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_SFD_exp3_exgaussian.qs"))
blmm_target_GD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_GD_exp3_exgaussian.qs"))
blmm_target_TVT_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_target_TVT_exp3_exgaussian.qs"))

# prepare effect summaries
blmm_target_FFD_exp3_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "Freq1")
blmm_target_FFD_exp3_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "Tracker1")
blmm_target_FFD_exp3_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "Freq1:Tracker1")

blmm_target_FFD_exp3_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "beta_Freq1")
blmm_target_FFD_exp3_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "beta_Tracker1")
blmm_target_FFD_exp3_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_FFD_exp3_exgaussian, "beta_Freq1:Tracker1")

blmm_target_GD_exp3_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "Freq1")
blmm_target_GD_exp3_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "Tracker1")
blmm_target_GD_exp3_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "Freq1:Tracker1")

blmm_target_GD_exp3_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "beta_Freq1")
blmm_target_GD_exp3_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "beta_Tracker1")
blmm_target_GD_exp3_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_GD_exp3_exgaussian, "beta_Freq1:Tracker1")

blmm_target_SFD_exp3_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "Freq1")
blmm_target_SFD_exp3_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "Tracker1")
blmm_target_SFD_exp3_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "Freq1:Tracker1")

blmm_target_SFD_exp3_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "beta_Freq1")
blmm_target_SFD_exp3_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "beta_Tracker1")
blmm_target_SFD_exp3_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_SFD_exp3_exgaussian, "beta_Freq1:Tracker1")

blmm_target_TVT_exp3_exgaussian_mu_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "Freq1")
blmm_target_TVT_exp3_exgaussian_mu_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "Tracker1")
blmm_target_TVT_exp3_exgaussian_mu_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "Freq1:Tracker1")

blmm_target_TVT_exp3_exgaussian_beta_Freq1_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "beta_Freq1")
blmm_target_TVT_exp3_exgaussian_beta_Tracker1_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "beta_Tracker1")
blmm_target_TVT_exp3_exgaussian_beta_interaction_effect <- brms_effect_summary(blmm_target_TVT_exp3_exgaussian, "beta_Freq1:Tracker1")

# save emmeans calculations for testing the marginal effect of frequency by tracker

marginal_effects_exp3_target_FFD <- emmeans(blmm_target_FFD_exp3_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp3_target_GD <- emmeans(blmm_target_GD_exp3_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp3_target_SFD <- emmeans(blmm_target_SFD_exp3_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

marginal_effects_exp3_target_TVT <- emmeans(blmm_target_TVT_exp3_exgaussian, ~ Freq | Tracker) %>% pairs() %>% gather_emmeans_draws() %>% mean_qi(.width = .95)

# make strings for printing in the manuscript 

marginal_effects_string_exp3_target_FFD <- format_contrast_string(marginal_effects_exp3_target_FFD)
marginal_effects_string_exp3_target_SFD <- format_contrast_string(marginal_effects_exp3_target_SFD)
marginal_effects_string_exp3_target_GD <- format_contrast_string(marginal_effects_exp3_target_GD)
marginal_effects_string_exp3_target_TVT <- format_contrast_string(marginal_effects_exp3_target_TVT)  

```


```{r}
#| label: tbl-exp3-target-word-means
#| echo: false
#| message: false
#| after-caption-space: 0pt
#| tbl-cap: "Mean first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 3 by eye-tracker and word frequency condition."
#| cache: true

# Calculate means and standard deviations for fixation time measures
target_words_exp3_means_table <- target_words_exp3 %>% 
  #filter(FFD > 80 & FFD < 1500) %>%
  group_by(Tracker, Freq) %>%
  summarise(
    mean_FFD = mean(FFD, na.rm = TRUE),
    sd_FFD = sd(FFD, na.rm = TRUE),
    mean_SFD = mean(SFD, na.rm = TRUE),
    sd_SFD = sd(SFD, na.rm = TRUE),
    mean_GD = mean(GD, na.rm = TRUE),
    sd_GD = sd(GD, na.rm = TRUE),
    mean_TVT = mean(TVT, na.rm = TRUE),
    sd_TVT = sd(TVT, na.rm = TRUE),
    #N = n() # N here is the number of correct trials within the RT filter
  ) %>%
  ungroup()

# use gt to make a table

target_words_exp3_means_table %>%
  gt(rowname_col = "Tracker") %>%
  cols_label(
   starts_with("mean") ~ "Mean",
   starts_with("sd") ~ "SD",
   "Freq" ~ "Frequency"
  ) %>%
  tab_spanner( # Add spanner columns for fixation time measures
    label = "FFD",
    columns = ends_with("FFD")
  ) %>%
  tab_spanner(
    label = "SFD",
    columns = ends_with("SFD")
  ) %>%
  tab_spanner(
    label = "GD",
    columns = ends_with("GD")
  ) %>%
  tab_spanner(
    label = "TVT",
    columns = ends_with("TVT")
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 0
  ) %>%
  tab_stubhead(label = "Tracker") %>%
  tab_source_note(source_note = md("Note: *FFD* = first fixation duration; *SFD* = single fixation duration; *GD* = gaze duration; *TVT* = total viewing time; SD = standard deviation. All means and standard deviations are reported in milliseconds (ms)."))

```

#### Target word analysis

@tbl-exp3-target-word-means shows the means and standard deviations for the four fixation time measures on target words in Experiment 3, while @tbl-eyelink-exp3-target-word-brms-modelsummary shows the results of the Bayesian linear mixed model for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT).

```{r}
#| label: tbl-eyelink-exp3-target-word-brms-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: true
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on target words in Experiment 3."

coef_map <- c("b_Intercept" = "Intercept (μ)",
              "b_Freq1" = "Frequency (μ)",
              "b_Tracker1" = "Tracker (μ)",
              "b_Freq1:Tracker1" = "Frequency × Tracker (μ)",
              "b_beta_Intercept" = "Intercept (β)",
              "b_beta_Freq1" = "Frequency (β)",
              "b_beta_Tracker1" = "Tracker (β)",
              "b_beta_Freq1:Tracker1" = "Frequency × Tracker (β)")

# Pass the map to the coef_map argument

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"

stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_target_FFD_exp3_exgaussian, SFD = blmm_target_SFD_exp3_exgaussian, GD = blmm_target_GD_exp3_exgaussian, TVT = blmm_target_TVT_exp3_exgaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
             coef_map = coef_map,
             gof_map = NA,
             output = "gt",
  
) |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))

```

#### Corpus-style analysis

```{r}
#| label: load-exp3-corpus-model-results
#| echo: false
#| message: false
#| warning: false
#| cache: true

# load the model results

blmm_corpus_FFD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_FFD_exp3_exgaussian.qs"))
blmm_corpus_SFD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_SFD_exp3_exgaussian.qs"))
blmm_corpus_GD_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_GD_exp3_exgaussian.qs"))
blmm_corpus_TVT_exp3_exgaussian <- qs_read(here("LAB-SPAIN", "models", "brms", "blmm_corpus_TVT_exp3_exgaussian.qs"))

# prepare effect summaries
blmm_corpus_FFD_exp3_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_FFD_exp3_exgaussian, "ctrzipf")
blmm_corpus_FFD_exp3_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_FFD_exp3_exgaussian, "Tracker1")
blmm_corpus_FFD_exp3_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_SFD_exp3_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_SFD_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_SFD_exp3_exgaussian, "ctrzipf")
blmm_corpus_SFD_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_SFD_exp3_exgaussian, "Tracker1")
blmm_corpus_SFD_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_SFD_exp3_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_GD_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "ctrzipf")
blmm_corpus_GD_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "Tracker1")
blmm_corpus_GD_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_GD_exp1_exgaussian, "ctrzipf:Tracker1")

blmm_corpus_TVT_exp1_exgaussian_freq_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "ctrzipf")
blmm_corpus_TVT_exp1_exgaussian_Tracker1_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "Tracker1")
blmm_corpus_TVT_exp1_exgaussian_interaction_effect <- brms_effect_summary(blmm_corpus_TVT_exp1_exgaussian, "ctrzipf:Tracker1")

# save emtrends calculations for testing the marginal effect of frequency by tracker

marginal_effects_exp3_corpus_FFD <- emtrends(blmm_corpus_FFD_exp3_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp3_corpus_GD <- emtrends(blmm_corpus_GD_exp3_exgaussian, "Tracker", "zipf")  %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp3_corpus_SFD <- emtrends(blmm_corpus_SFD_exp3_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
marginal_effects_exp3_corpus_TVT <- emtrends(blmm_corpus_TVT_exp3_exgaussian, "Tracker", "zipf") %>% gather_emmeans_draws() %>% mean_qi(.width = .95)
```


```{r}
#| label: tbl-exp3-corpus-modelsummary
#| echo: false
#| message: false
#| warning: false
#| cache: false
#| after-caption-space: 0pt
#| tbl-cap: "Coefficient estimates and 95% credible intervals (in square brackets) from Bayesian linear mixed models fitted to first fixation duration (FFD), single fixation duration (SFD), gaze duration (GD), and total viewing time (TVT) on all words (except for the first and last in each sentence) in Experiment 3. Estimates whose CI does not include 0 are marked in **bold**."

coef_map_corpus <- c("b_Intercept" = "Intercept (μ)",
              "b_ctrzipf" = "Zipf frequency (μ)",
              "b_Tracker1" = "Tracker (μ)",
              "b_ctrzipf:Tracker1" = "Frequency × Tracker (μ)",
              "b_beta_Intercept" = "Intercept (β)",
              "b_beta_ctrzipf" = "Zipf frequency (β)",
              "b_beta_Tracker1" = "Tracker (β)",
              "b_beta_ctrzipf:Tracker1" = "Frequency × Tracker (β)")

# Pass the map to the coef_map argument

est_string <- "{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', estimate)}{ifelse(conf.low * conf.high > 0, '**', '')}"

stat_string <- "[{ifelse(conf.low * conf.high > 0, '**', '')}{sprintf('%.3f', conf.low)}, {sprintf('%.3f', conf.high)}{ifelse(conf.low * conf.high > 0, '**', '')}]"

modelsummary(models = list(FFD = blmm_corpus_FFD_exp3_exgaussian, SFD = blmm_corpus_SFD_exp3_exgaussian, GD = blmm_corpus_GD_exp3_exgaussian, TVT = blmm_corpus_TVT_exp3_exgaussian),
             estimate = est_string,
             fmt = NULL,
             statistic = stat_string,
  
  # 2. Hide the default redundant estimate row
             coef_map = coef_map_corpus,
             gof_map = NA,
             output = "gt",
  
) |>  gt::fmt_markdown(columns = c("FFD", "SFD", "GD", "TVT"))

```

@tbl-exp3-corpus-modelsummary shows the results of the corpus-style Bayesian linear mixed models for the four fixation time measures (first fixation duration, FFD; single fixation duration, SFD; gaze duration, GD; total viewing time, TVT) on all words in the sentences (except for the first and last word in each sentence) in Experiment 3.

# Discussion

## Limitations and Future Directions

## Conclusion

# References

<!-- References will auto-populate in the refs div below -->

::: {#refs}
:::

# This Section Is an Appendix {#apx-a}


# Another Appendix {#apx-b}